---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###2.

**(a)**

```{r}
suppressMessages(library(dplyr))
pwt <- read.csv("~/Documents/2017-18/ECON241/Problem_Sets/ps2/pwt_and_bl_excerpt.csv")
pwt <- pwt %>% mutate(humancap = ifelse(yr_sch <= 4, 1*1.134^(yr_sch), 
                                        ifelse(yr_sch <= 8, 1*(1.134^4)*1.101^(yr_sch-4), 
                                               1*(1.134^4)*(1.101^4)*1.068^(yr_sch-8))), 
                      gdpPercap = rgdpna/emp)
```

**(b)**

```{r}
US_Korea <- pwt %>% filter(country %in% c("United States", "Republic of Korea"))
predict1 <- US_Korea[1,10]/US_Korea[2,10]
actual1 <- US_Korea[1,11]/US_Korea[2,11]
```

Predicted income ratio ($\frac{h~Korea~}{h~US~}$) = `r predict1`
\newline
Actual income ratio ($\frac{y~Korea~}{y~US~}$) = `r actual1`

**(c)**

```{r}
US_Korea <- US_Korea %>% mutate(capPercap = rkna/emp, 
                                savingsRate = (delta+n)*capPercap/gdpPercap)
predict2 <- (US_Korea[1,13]/US_Korea[2,13])^(1/2)
```

Assuming $\alpha$ = $\frac{1}{3}$,
predicted income ratio ($\sqrt{\frac{\frac{\gamma~Korea}{\delta+n}}{\frac{\gamma~US}{\delta+n}}}$) = `r predict2`

**(d)**

```{r}
predict3 <- predict1*predict2
```

Predicted income ratio ($\frac{h~Korea~}{h~US~}$ $\times$
$\sqrt{\frac{\frac{\gamma~Korea}{\delta+n}}{\frac{\gamma~US}{\delta+n}}}$)= `r predict3`

**(e)**

We may assume that there is a huge discrepancy in productivity between the two countries. 
